### 2016-07-08 2nd_round_comments/DVCS-CAN-Meeting-Comments.tex
added figure for the 4D background subtraction

Figs 1-4 of \url{https://clasweb.jlab.org/rungroups/lowq/wiki/images/a/a3/Final_1st_round_comments.pdf} 
Tighter $edist$ cut [-2,+3 mm].
Otherwise, even if you do not show it in the CAN, mention in one line that a 
specific study was done.
\item Miscellaneous:
   \begin{enumerate}
      \item 4-D dependences of the ratio R: the statement that the integrated R's 
    are flat is disputable (see Figs 4.16 and 4.17), but we are ready to accept 
    that the effect discussed is small and taken care of in the systematic 
    errors.
 \item not convinced that comparing 9 phi-bins to 11 is a definitive answer, 
    when not applying any finite bin size correction. But again, in view of the 
    size of statistical and systematic errors, would accept that.
 \item Your Eq.(4) of "answer" is probably wrong. For our own understanding, 
   look into this argument again.
\item ...
   \end{enumerate}

>>>>

Figs 1-4 of \url{https://clasweb.jlab.org/rungroups/lowq/wiki/images/a/a3/Final_1st_round_comments.pdf} 
Tighter $edist$ cut [-2,+3 mm].
Otherwise, even if you do not show it in the CAN, mention in one line that a 
specific study was done.
\item Miscellaneous:
   \begin{enumerate}
      \item 4-D dependences of the ratio R: the statement that the integrated R's 
    are flat is disputable (see Figs 4.16 and 4.17), but we are ready to accept 
    that the effect discussed is small and taken care of in the systematic 
    errors.
    \begin{figure}[tbp]
    \includegraphics[height=6.6cm]{fig/BSA_Coherent_xB.png}
    \includegraphics[height=6.6cm]{fig/diff_BSA_Coherent_xB.png}
    \caption{On top: the reconstruct coherent beam-spin asymmetries as a 
    function of $\phi$ in $x_{B}$ bins using 2D (in blue) and 4D (in green) 
 background subtraction.  On bottom: the difference between the two asymmetries 
 as a function of $\phi$.}
    \label{fig:coh_binning}
    \end{figure}

    \begin{figure}[tbp]
    \includegraphics[height=5.6cm]{fig/BSA_InCoherent_xB.png}
    \includegraphics[height=5.6cm]{fig/diff_BSA_InCoherent_xB.png}
    \caption{On top: the reconstruct incoherent beam-spin asymmetries using 2D   
    (in blue) and 4D (in green) background subtraction. On bottom: the 
 difference between the two asymmetries as a function of $\phi$.}
    \label{fig:incoh_binning}
    \end{figure}

 \item not convinced that comparing 9 phi-bins to 11 is a definitive answer, 
    when not applying any finite bin size correction. But again, in view of the 
    size of statistical and systematic errors, would accept that.
 \item Your Eq.(4) of "answer" is probably wrong. For our own understanding, 
   look into this argument again.
\item ...
   \end{enumerate}

### 2016-07-08 analysis-note-v2/analysis-2.tex
added figure for the 4D background subtraction

For the second technique, in fact there is only one event generator available, presented in section \ref{Event_generator}. Nevertheless, one can still use this method by generating events with or without the cross section parametrization. In the absence of the parametrization, the generated events are flat in the four kinematic variables ($Q^2$, $-t$, $x_B$, $\phi$). The calculated coherent and incoherent acceptance ratios (R) with and without the cross section parametrization are shown in figure \ref{fig:accep_ratio_sys_uncer}. One can see that the difference between the calculated acceptance ratios is almost constant. Thus, we can conclude that the first method of taking $\pm$20$\%$ on R is is an adequate way to obtain an estimation of the systematic uncertainty associated to the calculated acceptance ratios.
\begin{figure}[h!]
\includegraphics[scale=0.34]{fig_results/coh_accp_ratio_phi.png}
\includegraphics[scale=0.34]{fig_results/incoh_accp_ratio_phi.png}
\caption{The coherent (on the top) and the incoherent (on the bottom) acceptance ratios ($R$) as function of the angle $\phi$. In both plots, the blue (red) points are the ratios with (without) the cross section parametrization.} 
\label{fig:accep_ratio_sys_uncer}
\end{figure}

@@

%\paragraph{Beam asymmetry}
%The injector of JLab produces electrons with positive and negative helicities in equal %time in principle. To ensure this equality between the two helicity configurations., %figure \ref{fig:beam_charge} shows the deposited charge ratio of the positive helicity %electrons to the negative ones in the individual runs. A 2$\%$  maximum deviation from %one. Thus, the integrated beam charge ratio induces 1.1$\%$ systematic uncertainty to %$A_{LU}$ on both DVCS channels.\\
%\begin{figure}[h!]
%\hspace{-0.3in}
%\includegraphics[scale=0.4]{fig_bsa/qplus_qminus_RunNum.png}
%\caption{The beam charge ratio between the positive and the negative helicites.} 
%\label{fig:beam_charge}

@@

\begin {table}[!h]
\begin{center}
\begin{tabular}{|l|l|l|l|}
\hline
Systematic source &  Coherent channel  & Incoherent channel &Type of systematic 
error\\
\hline
DVCS cuts & ~~~~~8 $\%$ &  ~~~~~6 $\%$ & bin to bin\\
\hline
Data binning & ~~~~~5.1$\%$ & ~~~~~7.1$\%$ &bin to bin\\
\hline
Beam polarization &  ~~~~~3.5$\%$ &  ~~~~~3.5$\%$& Normalization\\
\hline
Acceptance ratio &  ~~~~~0.6$\%$ &  ~~~~~2.0$\%$ &bin to bin\\
\hline
%Beam charge asymmetry &  ~~~~~1.1$\%$&  ~~~~~1.1$\%$\\
%\hline
Radiative corrections &  ~~~~~0.1$\%$ & ~~~~~0.1$\%$ & bin to bin\\
\hline
\textbf{Total} &  ~~~~~\textbf{10.1}$\%$ &   ~~~~~\textbf{10.1}$\%$ &bin to 
bin\\
\hline
\end{tabular}
\caption{ The systematic uncertainties on the measured coherent and incoherent beam-spin asymmetries at $\phi = 90^{\circ}$.}
\label{Table:systematic_uncertainties}
\end{center}
\end{table}

>>>>

For the second technique, in fact there is only one event generator available, 
presented in section \ref{Event_generator}. Nevertheless, one can still use 
this method by generating events with or without the cross section 
parametrization. In the absence of the parametrization, the generated events 
are flat in the four kinematic variables ($Q^2$, $-t$, $x_B$, $\phi$). The 
calculated coherent and incoherent acceptance ratios (R) with and without the 
cross section parametrization are shown in figure 
\ref{fig:accep_ratio_sys_uncer}. One can see that the difference between the 
calculated acceptance ratios is almost constant. Thus, we can conclude that the 
first method of taking $\pm$20$\%$ on R is is an adequate way to obtain an 
estimation of the systematic uncertainty associated to the calculated 
acceptance ratios.
\begin{figure}[h!]
\includegraphics[scale=0.34]{fig_results/coh_accp_ratio_phi.png}
\includegraphics[scale=0.34]{fig_results/incoh_accp_ratio_phi.png}
\caption{The coherent (on the left) and the incoherent (on the right) 
acceptance ratios ($R$) as function of the angle $\phi$. In both plots, the 
blue (red) points are the ratios with (without) the cross section 
parametrization.} \label{fig:accep_ratio_sys_uncer}
\end{figure}

@@

%\paragraph{Beam asymmetry}
%The injector of JLab produces electrons with positive and negative helicities 
%in equal %time in principle. To ensure this equality between the two helicity 
%configurations., %figure \ref{fig:beam_charge} shows the deposited charge 
%ratio of the positive helicity %electrons to the negative ones in the 
%individual runs. A 2$\%$  maximum deviation from %one. Thus, the integrated 
%beam charge ratio induces 1.1$\%$ systematic uncertainty to %$A_{LU}$ on both 
%DVCS channels.\\
%\begin{figure}[h!]
%\hspace{-0.3in}
%\includegraphics[scale=0.4]{fig_bsa/qplus_qminus_RunNum.png}
%\caption{The beam charge ratio between the positive and the negative helicites.} 
%\label{fig:beam_charge}

@@

\begin {table}[!h]
\begin{center}
\begin{tabular}{|l|l|l|l|}
\hline
Systematic source &  Coherent channel  & Incoherent channel &Type of systematic 
error\\
\hline
DVCS cuts & ~~~~~8 $\%$ &  ~~~~~6 $\%$ & bin to bin\\
\hline
Data binning & ~~~~~5.1$\%$ & ~~~~~7.1$\%$ &bin to bin\\
\hline
Beam polarization &  ~~~~~3.5$\%$ &  ~~~~~3.5$\%$& Normalization\\
\hline
Acceptance ratio &  ~~~~~0.6$\%$ &  ~~~~~2.0$\%$ &bin to bin\\
\hline
%Beam charge asymmetry &  ~~~~~1.1$\%$&  ~~~~~1.1$\%$\\
%\hline
Radiative corrections &  ~~~~~0.1$\%$ & ~~~~~0.1$\%$ & bin to bin\\
\hline
\textbf{Total} &  ~~~~~\textbf{10.1}$\%$ &   ~~~~~\textbf{10.1}$\%$ &bin to 
bin\\
\hline
\end{tabular}
\caption{The systematic uncertainties on the measured coherent and incoherent 
beam-spin asymmetries at $\phi = 90^{\circ}$.}
\label{Table:systematic_uncertainties}
\end{center}
\end{table}
